Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-12-23 latex/ms.tex
finish Results section, #13

Our simulator can handle the situation with or without invasive sampling. Invasive sampling potentially affect the $m$ since sampled parents in the population 1 have no chance to move to the population 2 and thus those parents cannot be sampled. In this case, $m$ should be defined by $M/(N_1-n_{P,1})$ not by $M/N_1$, although it does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).

\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
\subsection{Invasive sampling}

\subsection{Case of $N_1 \neq N_2$}

>>>>

Our simulator can handle the situation with or without invasive sampling. Invasive sampling potentially affects the degree of $m$ since sampled parents in the population 1 have no chance to move to the population 2 and thus those parents cannot be sampled. In this case, $m$ should be defined by $M/(N_1-n_{P,1})$ not by $M/N_1$, although it does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).

Finally, we investigated the situation in which the parental number in the population 1 is much more than in the population 2 (i.e., $N_1 \gg N_2$) and thus migrants are large proportion of $N_2$. In such a setting, e.g., $(N_1,N_2,M)=(10^4,10^3,500)$, we confirmed the same property of ${\hat M}$s to the situation $N_1 = N_2$, as demonstrated in {\bf Table S1} ({\bf Supporting Information}), suggesting the robustness of ${\hat M}$s in heterogeneous population sizes.

\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
